\renewcommand{\bibname}{REFERENCES}
\begin{thebibliography}{10}
\addcontentsline{toc}{chapter}{REFERENCES}
\baselineskip
20pt

% CHAPTER 1

% \bibitem{biometric_comparison} Hietmeyer, R., \texti{Biometric identification promises fast and secure processing of airline passengers}, ICAO J. 55(9), 10–11 (2000)

\bibitem{checkin_system_fr} Qi Liu, Hong Li, Yan Hu and Limin Sun, \textit{"A Check-in System Leveraging Face Recognition"}, 2018 IEEE Confs on Internet of Things, Green Computing and Communications, Cyber, Physical and Social Computing, Smart Data, Blockchain, Computer and Information Technology, Congress on Cybermatics.

\bibitem{hog_fr} Qiang Zhu, Shai Avidan, Mei-Chen Yeh, and Kwang-Ting Cheng, \textit{“Fast Human Detection Using a Cascade of Histograms of Oriented Gradients”}, In Conference on Computer Vision And Pattern Recognition, 2006

\bibitem{mmod} Davis E. King, \textit{"Max-Margin Object Detection”}, In Conference on Computer Vision And Pattern Recognition, 2015

\bibitem{center_face} Xu, Yuanyuan and Yan, Wan and Sun, Haixin and Yang, Genke and Luo, Jiliang, \textit{“CenterFace: Joint Face Detection and Alignment Using Face as Point”}, In Conference on Computer Vision And Pattern Recognition, 2019

\bibitem{dev_optimal_checkin_system} Pingping Chen, \textit{"Development and Optimization of Check-in System Based on Face Recognition Technology"}, et al 2020 IOP Conf. Ser.: Mater. Sci. Eng. 782 052022.

% CHAPTER 2
\bibitem{mmod_1} R. Fletcher. \textit{"Practical Methods of Optimization, Second Edition"}. John Wiley & Sons, 1987.

\bibitem{mmod_2} C. Huang and R. Nevatia. \textit{"High performance object detection by collaborative learning of joint ranking of granules features"}. In Computer Vision and Pattern Recognition, 2010.

\bibitem{mmod_3} X. Zhu and D. Ramanan. \textit{"Face detection, pose estimation, and landmark localization in the wild"}. In Computer Vision and Pattern Recognition, 2012.

\bibitem{mobile_net} M. Sandler, A. G. Howard, M. Zhu, A. Zhmoginov, and L. Chen, \textit{“Inverted residuals and linear bottlenecks: Mobile networks for classification, detection and segmentation”}, CoRR, vol. abs/1801.04381, 2018. [Online]. Available: \href{http://arxiv.org/abs/1801.04381}

\bibitem{fpn} T. Lin, P. Dollár, R. B. Girshick, K. He, B. Hariharan, and S. J. Belongie,, \textit{“Feature pyramid networks for object detection”}, CoRR, vol. abs/1612.03144, 2016. [Online]. Available: \href{http://arxiv.org/abs/1612.03144}

\bibitem{dlib_library} D. E. King, \texti{Dlib-ml: A machine learning toolkit}, The Journal of Machine Learning Research, vol. 10, pp. 1755–1758, 2009

\bibitem{compare}Thompson, Cindi. “Open Source Toolkits for Speech Recognition.” Silicon Valley Data Science, 10 May 2018, \href{https://www.svds.com/open-source-toolkits-speech-recognition/}{https://www.svds.com/open-source-toolkits-speech-recognition/}

% CHAPTER 3
\bibitem{mic_v2}{ReSpeaker Mic Array v2.0 Specifications} \href{https://wiki.seeedstudio.com/ReSpeaker_Mic_Array_v2.0/}

\bibitem{jetpack_nvidia}{“Introduction to JetPack :: NVIDIA JetPack Documentation.”}
\href{https://docs.nvidia.com/jetson/jetpack/introduction/index.html}

\bibitem{iothub_concept}{“What is Azure IoT Hub | Microsoft Docs”}
\href{https://docs.microsoft.com/en-us/azure/iot-hub/about-iot-hub}

\bibitem{direct_method}{“Understand Azure IoT Hub direct methods | Microsoft Docs”}
\href{https://docs.microsoft.com/en-us/azure/iot-hub/iot-hub-devguide-direct-methods}

\bibitem{eventhub_concept}{“What is Azure Event Hubs? - a Big Data ingestion service”}
\href{https://docs.microsoft.com/en-us/azure/event-hubs/event-hubs-about}


% CHPATER 4










%CHAPTER2
\bibitem {} Shmyrev, N., 2020. Basic Concepts Of Speech Recognition. [online] CMUSphinx Open Source Speech Recognition. Available at: \href{https://cmusphinx.github.io/wiki/tutorialconcepts/}{https://cmusphinx.github.io/wiki/tutorialconcepts/} 
\bibitem {} Jinyu Li and Yifan Gong. “Robust Automatic Speech Recognition.” 2016. 
\bibitem{wuw}V. Këpuska, J. Breitfeller, Wake-up-word application for first responder communication enhancement, Proc. SPIE 6201, pp. 62011E, 2006.  doi:10.1117/12.666025

\bibitem{foss}James, Simon. “10 Good Open Source Speech Recognition Systems [2020].” FOSS Post, 23 Aug. 2020,\href{https://fosspost.org/open-source-speech-recognition-2020/}{https://fosspost.org/open-source-speech-recognition-2020/}. 
\bibitem{deepspeech}Firmansysah, Muhammad Hafidth, et al. A.I. Based Embedded Speech to Text Using Deepspeech. 25 Feb. 2020,
\href{https://arxiv.org/pdf/2002.12830.pdf/}{https://arxiv.org/pdf/2002.12830.pdf}. 

\end{thebibliography}